First Season MWA EoR Power Spectrum Results at Redshift 7

### 2016-06-30 ms.tex
Updated plot reference after color change

Of the 1,029 observations calibrated and used by the FHD pipeline, the RTS$+$CHIPS 
pipeline successfully calibrated and included 1,003. The remainder failed to calibrate 
successfully, potentially due to adverse ionospheric conditions. The data were divided into the 
same three redshift bins, and the 2D and 1D power spectra formed. Table \ref{tbl:limits} 
displays comparison 2-sigma upper limits, demonstrating broad consistency between the 
pipelines. The RTS$+$CHIPS best limits appear at a lower $k$ bin than FHD$+$\eppsilon, 
owing to the different structure of the foreground leakage for the two pipelines. 
Figure~\ref{fig:slices}, which shows the resulting FHD$+$\eppsilon slices in $k_\parallel$ and 
$k_\bot$, also displays the equivalent power profiles for RTS$+$CHIPS. The comparison 
pipeline shows significantly more power at low $k_\bot$, consistent with no diffuse model 
being subtracted from the data. Aside from this area, the two pipelines show consistent 
results. Figure~\ref{fig:ps_comparison} compares the 1D power from both pipelines for the 
three central redshifts studied in this work. The magenta line reproduces the FHD$+$\eppsilon 
results from Figure~\ref{fig:1d_ps}, while the blue line plots the equivalent RTS$+$CHIPS 
results (with coarse band harmonics included). Despite the differences in the two pipelines, 
they produce consistent power across a range of scales, supporting the robustness of the 
results.

>>>>

Of the 1,029 observations calibrated and used by the FHD pipeline, the RTS$+$CHIPS 
pipeline successfully calibrated and included 1,003. The remainder failed to calibrate 
successfully, potentially due to adverse ionospheric conditions. The data were divided into the 
same three redshift bins, and the 2D and 1D power spectra formed. Table \ref{tbl:limits} 
displays comparison 2-sigma upper limits, demonstrating broad consistency between the 
pipelines. The RTS$+$CHIPS best limits appear at a lower $k$ bin than FHD$+$\eppsilon, 
owing to the different structure of the foreground leakage for the two pipelines. 
Figure~\ref{fig:slices}, which shows the resulting FHD$+$\eppsilon slices in $k_\parallel$ and 
$k_\bot$, also displays the equivalent power profiles for RTS$+$CHIPS. The comparison 
pipeline shows significantly more power at low $k_\bot$, consistent with no diffuse model 
being subtracted from the data. Aside from this area, the two pipelines show consistent 
results. Figure~\ref{fig:ps_comparison} compares the 1D power from both pipelines for the 
three central redshifts studied in this work. The magenta line reproduces the FHD$+$\eppsilon 
results from Figure~\ref{fig:1d_ps}, while the gray line plots the equivalent RTS$+$CHIPS 
results (with coarse band harmonics included). Despite the differences in the two pipelines, 
they produce consistent power across a range of scales, supporting the robustness of the 
results.
